---
title: "iemisctext: Example Analysis using the tm package"
author: "Irucka Embry"
date: "`r Sys.Date()`"
lang: en-us
urlcolor: blue
output:
  rmarkdown::pdf_document:
    highlight: kate
    toc: true
    latex_engine: xelatex
vignette: >
  %\VignetteIndexEntry{iemisctext Examples using the tm package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\bigskip

# Examples

## Example 1

```{r, warning = FALSE, message = FALSE, tidy = TRUE}
install.load::load_package("iemisctext", "tm")
# load needed packages using the load_package function from the install.load package (it is assumed that you have already installed these packages)


# appeal_womanhood_world
data(appeal_womanhood_world)

# create a document term matrix of appeal_womanhood_world
a <- DocumentTermMatrix(appeal_womanhood_world)

# find terms used > 5 times
findFreqTerms(a, 5)

# Zipf's law
Zipf_plot(a)




# anarchy
data(anarchy)

# create a document term matrix of anarchy
a <- DocumentTermMatrix(anarchy)

# find terms used > 5 times
findFreqTerms(a, 5)

# Zipf's law
Zipf_plot(a)




# war_prayer
data(war_prayer)

# create a document term matrix of war_prayer
wp <- DocumentTermMatrix(war_prayer)

# find terms used > 5 times
findFreqTerms(wp, 5)

# Zipf's law
Zipf_plot(wp)




# war_racket
data(war_racket)

# create a document term matrix of war_racket
wr <- DocumentTermMatrix(war_racket)

# find terms used > 5 times
findFreqTerms(wr, 5)

# Zipf's law
Zipf_plot(wr)




# connect_dots
data(connect_dots)

# create a document term matrix of connect_dots
cd <- DocumentTermMatrix(connect_dots)

# find terms used > 5 times
findFreqTerms(cd, 5)

# Zipf's law
Zipf_plot(cd)




# us_them
data(us_them)

# create a document term matrix of us_them
ut <- DocumentTermMatrix(us_them)

# find terms used > 5 times
findFreqTerms(ut, 5)

# Zipf's law
Zipf_plot(ut)




# climate_strange
data(climate_strange)

# create a document term matrix of climate_strange
cs <- DocumentTermMatrix(climate_strange)

# find terms used > 5 times
findFreqTerms(cs, 5)

# Zipf's law
Zipf_plot(cs)
```

\bigskip
\bigskip
\bigskip
\bigskip

## Example 2

```{r eval = FALSE}
install.load::load_package("iemisctext", "tm")
# load needed packages using the load_package function from the install.load package (it is assumed that you have already installed these packages)

# appeal_womanhood_world
data(appeal_womanhood_world)

# View text representation of appeal_womanhood_world
inspect(appeal_womanhood_world[[1]])



# anarchy
data(anarchy)

# View text representation of anarchy
inspect(anarchy[[1]])




# war_prayer
data(war_prayer)

# View text representation of war_prayer
inspect(war_prayer[[1]])




# war_racket
# Example 2

data(war_racket)

# View text representation of war_racket
inspect(war_racket[[1]])




# connect_dots
data(connect_dots)

# View text representation of connect_dots
inspect(connect_dots[[1]])




# us_them
data(us_them)

# View text representation of us_them
inspect(us_them[[1]])




# climate_strange
data(climate_strange)

# View text representation of climate_strange
inspect(climate_strange[[1]])
```

\bigskip
\bigskip

# EcoC²S Links

EcoC²S Home -- https://www.ecoccs.com/  
About EcoC²S -- https://www.ecoccs.com/about-ecoc2s.html  
Services -- https://www.ecoccs.com/services.html  
1 Stop Shop -- https://www.ecoccs.com/other-biz.html  
Products -- https://www.questionuniverse.com/products.html  
Media -- https://www.ecoccs.com/media.html  
Resources -- https://www.ecoccs.com/resources.html  
R Trainings and Resources provided by EcoC²S (Irucka Embry, E.I.T.) -- https://www.ecoccs.com/rtraining.html  

\bigskip
\bigskip

# Copyright and License

All R code written by Irucka Embry is distributed under the GPL-3 (or later) license, see the [GNU General Public License {GPL} page](https://www.gnu.org/licenses/gpl-3.0.html).  

All written content originally created by Irucka Embry is copyrighted under the Creative Commons Attribution-ShareAlike 4.0 International license. All other written content retains the copyright of the original author(s).  

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International license](https://creativecommons.org/licenses/by-sa/4.0/).  
